---
title: "README"
output: github_document
---

# Hospital Quality Comparison

Download here: [HospitalCompare_Data](https://d396qusza40orc.cloudfront.net/rprog%2Fdata%2FProgAssignment3-data.zip)

This data come from the Hospital Compare web site (http://hospitalcompare.hhs.gov)
run by the U.S. Department of Health and Human Services. The purpose of the web site is to provide data and information about the quality of care at over 4,000 Medicare-certified hospitals in the U.S. This dataset essentially covers all major U.S. hospitals. This dataset is used for a variety of purposes, including determining whether hospitals should be fined for not providing high quality care to patients (see http://goo.gl/jAXFX for some background on this particular topic).

## Data set

The Hospital Compare web site contains a lot of data and we will only look at a small subset for this
assignment. The link data files contains three files:

* outcome-of-care-measures.csv: Contains information about 30-day mortality and readmission rates
for heart attacks, heart failure, and pneumonia for over 4,000 hospitals.

* hospital-data.csv: Contains information about each hospital.

* Hospital_Revised_Flatfiles.pdf: Descriptions of the variables in each file (i.e the code book)

### Data subset:

A description of the variables in each of the files is in the included PDF file named Hospital_Revised_Flatfiles.pdf.
This document contains information about many other files that are not included in this dataset. This data-subset is focus on the variables for Number 19 (“Outcome of Care Measures.csv”) and Number 11 (“Hospital Data.csv”).

## Hospital Comparison Analysis:

### U.S Hospitals 30-day mortality rates for heart attack

```{r,echo=FALSE,warning=FALSE,message=FALSE}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
outcome[, 11] <- as.numeric(outcome[, 11])
hist(outcome[, 11],
     main=NULL,
     xlab="30-day death rates from heart attack",
     ylab= "Hospitals Frequency",
     border="black",
     col="red")
```

### Finding the best hospital in a state (best_hospital.R)

The function reads the outcome-of-care-measures.csv file and returns a character vector with the name of the hospital that has the best (i.e. lowest) 30-day mortality for the specified outcome in that state. The hospital name is the name provided in the Hospital.Name variable. The outcomes can be one of “heart attack”, “heart failure”, or “pneumonia”. Hospitals that do not have data on a particular outcome should be excluded from the set of hospitals when deciding the rankings.

The function check the validity of its arguments. If an invalid state value is passed to best, the function should throw an error via the stop function with the exact message “invalid state”. If an invalid outcome value is passed to best, the function should throw an error via the stop function with the exact message “invalid outcome”.

Here is some sample output from the function:

```{r,warning=FALSE,message=FALSE,error=TRUE}
source("best_hospital.R")
best("TX", "heart attack")
best("TX", "heart failure")
best("BB", "heart attack")
best("NY", "hert attack")
```

### Ranking hospitals by outcome in a state (rank_hospital.R)

This function called rankhospital takes three arguments: the 2-character abbreviated name of a state (state), an outcome (outcome), and the ranking of a hospital in that state for that outcome (num).
The function reads the outcome-of-care-measures.csv file and returns a character vector with the name
of the hospital that has the ranking specified by the num argument.

The function check the validity of its arguments. If an invalid state value is passed to rankhospital, the function will send an error via the stop function with the exact message “invalid state”. If an invalid outcome value is passed to rankhospital, the function will send an error via the stop function with the exact message “invalid outcome”.

```{r,warning=FALSE,message=FALSE}
source("rank_hospital.R")
rankhospital("TX", "heart failure", 4)
rankhospital("MD", "heart attack", "worst")
```

Ranking all the hospitals (rank_all.R)

The function called rankall takes two arguments: an outcome name (outcome) and a hospital ranking (num). The function reads the outcome-of-care-measures.csv file and returns a 2-column data frame containing the hospital in each state that has the ranking specified in num. 
For example the function call rankall("heart attack", "best") would return a data frame containing the names of the hospitals that are the best in their respective states for 30-day heart attack death rates. The function will return a value for every state (some may be NA). The first column in the data frame is named hospital, which contains the hospital name, and the second column is named state, which contains the 2-character abbreviation for the state name. Hospitals that do not have data on a particular outcome will be excluded from the set of hospitals when deciding the rankings.

```{r,warning=FALSE,message=FALSE}
source("rank_all.R")
head(rankall("heart attack", 20), 10)
tail(rankall("pneumonia", "worst"), 3)
```

